Climate indicators

### 2023-02-27 DRAFT_climate_indicators.Rmd
failed execution

```{r}
path <- path <- ifelse(dir == "C:", 
      "R:/",
      "/data/R/")

@@

  tic("init")
  temp <- stars::read_ncdf(paste(path2, var="tg"))
  year_temp <- year(st_get_dimension_values(temp, "time")[1])
  start <- ym(paste(year_temp, start_month, sep="-"))
  end <-  ym(paste(year_temp, end_month, sep="-"))
  myInterval <- interval(start, end)
  toc()

@@

  tic("c")
  real_temp_summer <- c(temp, real_temp_summer)
  rm(temp)
  toc()
}
```

>>>>

```{r, warning=F}
path <- path <- ifelse(dir == "C:", 
      "R:/",
      "/data/R/")

@@

  tic("init")
  temp <- stars::read_ncdf(paste(myFiles[i]), var="tg")
  year_temp <- year(st_get_dimension_values(temp, "time")[1])
  start <- ym(paste(year_temp, start_month, sep="-"))
  end <-  ym(paste(year_temp, end_month, sep="-"))
  myInterval <- interval(start, end)
  toc()

@@

  tic("c")
  real_temp_summer <- c(temp, real_temp_summer)
  rm(temp)
  toc()
}
#
#tic("execute")
#real_temp_summer <- st_as_stars(real_temp_summer)
#toc()

write_stars(real_temp_summer, "P:/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/dummy_data/real_temp_summer.tif")
```

```{r}
dim(real_temp_summer)
st_get_dimension_values(real_temp_summer, "time")
```
